Brownian Dynein Model

### 2015-07-24 latex/derivation.tex
Add another attempt at solving angular velocities to derivation.tex.

\section{Cartesian from Angular Coordinates}
\begin{align}
  X_{bl} &= 0 \\
  X_{ml} &= X_{bl}+L_{t}\cos(\Theta_{bl}) \\
  X_{t}  &= X_{ml}+L_{s}\cos(\Theta_{ml}) \\
  X_{mr} &= X_{t} +L_{s}\cos(\Theta_{mr}-\pi) \\
  X_{br} &= X_{mr}+L_{t}\cos(\Theta_{br}-\pi)
\end{align}

@@

\section{Cartesian Velocities}
\begin{align}
  \dot{X}_{bl} &= 0 \\
  \dot{X}_{ml} &= \dot{X}_{bl} + L_{t}\sin(\Theta_{bl})      \dot{\Theta}_{bl} \\
  \dot{X}_{t } &= \dot{X}_{ml} + L_{s}\sin(\Theta_{ml})      \dot{\Theta}_{ml} \\
  \dot{X}_{mr} &= \dot{X}_{t } + L_{s}\sin(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} \\
  \dot{X}_{br} &= \dot{X}_{mr} + L_{t}\sin(\Theta_{br}-\pi)  \dot{\Theta}_{br}
\end{align}

@@

\section{Cartesian Velocities (expanded)}
\begin{align}
  \dot{X}_{bl} &= 0 \\
  \dot{X}_{ml} &= L_{t}\sin(\Theta_{bl})  \dot{\Theta}_{bl} \\
  \dot{X}_{t } &= L_{t}\sin(\Theta_{bl})  \dot{\Theta}_{bl} + L_{s}\sin(\Theta_{ml})      \dot{\Theta}_{ml} \\
  \dot{X}_{mr} &= L_{t}\sin(\Theta_{bl})  \dot{\Theta}_{bl} + L_{s}\sin(\Theta_{ml})      \dot{\Theta}_{ml} + L_{s}\sin(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} \\
  \dot{X}_{br} &= L_{t}\sin(\Theta_{bl})  \dot{\Theta}_{bl} + L_{s}\sin(\Theta_{ml})      \dot{\Theta}_{ml} + L_{s}\sin(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} + L_{t}\sin(\Theta_{br}-\pi)  \dot{\Theta}_{br}
\end{align}

@@

  \section{Brownian Equations}
\begin{align}  
  \dot{X}_{bl} &= 0 \\
  \dot{X}_{ml} &= \frac{1}{\gamma} \Big(F_{xml} + \mn \lambda_{ls}(X_{ml} - X_{bl}) + \lambda_{lt}(X_{t } - X_{ml}) \Big) + R_{xml} \\
  \dot{X}_{t } &= \frac{1}{\gamma} \Big(F_{xt } + \mn \lambda_{lt}(X_{t } - X_{ml}) + \lambda_{rt}(X_{mr} - X_{t }) \Big) + R_{xt } \\
  \dot{X}_{mr} &= \frac{1}{\gamma} \Big(F_{xmr} + \mn \lambda_{rt}(X_{mr} - X_{t }) + \lambda_{rs}(X_{br} - X_{mr}) \Big) + R_{xmr} \\
  \dot{X}_{br} &= \frac{1}{\gamma} \Big(F_{xbr} + \mn \lambda_{rs}(X_{br} - X_{mr})                                 \Big) + R_{xbr}
\end{align}

@@

  \section{System of Equations}

@@

\section{System after Addition to simplify RHS}

@@

\section{Solution for $\dot{\Theta}_{br}$}

@@

>>>>

\section{Cartesian from Angular Coordinates}
This section lays out the definitions of the coordinates of the Dynein model. \\
\begin{align}
  X_{bl} &= 0 \\
  X_{ml} &= X_{bl}+L_{t}\cos(\Theta_{bl}) \\
  X_{t}  &= X_{ml}+L_{s}\cos(\Theta_{ml}) \\
  X_{mr} &= X_{t} +L_{s}\cos(\Theta_{mr}-\pi) \\
  X_{br} &= X_{mr}+L_{t}\cos(\Theta_{br}-\pi)
\end{align}

@@

\section{Cartesian Velocities}
This section shows the velocity definitions. \\
\begin{align}
  \dot{X}_{bl} &= 0 \\
  \dot{X}_{ml} &= \dot{X}_{bl} + L_{t}\sin(\Theta_{bl})      \dot{\Theta}_{bl} \\
  \dot{X}_{t } &= \dot{X}_{ml} + L_{s}\sin(\Theta_{ml})      \dot{\Theta}_{ml} \\
  \dot{X}_{mr} &= \dot{X}_{t } + L_{s}\sin(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} \\
  \dot{X}_{br} &= \dot{X}_{mr} + L_{t}\sin(\Theta_{br}-\pi)  \dot{\Theta}_{br}
\end{align}

@@

\section{Cartesian Velocities (expanded)}
This section expands the above definitions. \\
\begin{align}
  \dot{X}_{bl} &= 0 \\
  \dot{X}_{ml} &= L_{t}\sin(\Theta_{bl})  \dot{\Theta}_{bl} \\
  \dot{X}_{t } &= L_{t}\sin(\Theta_{bl})  \dot{\Theta}_{bl} + L_{s}\sin(\Theta_{ml})      \dot{\Theta}_{ml} \\
  \dot{X}_{mr} &= L_{t}\sin(\Theta_{bl})  \dot{\Theta}_{bl} + L_{s}\sin(\Theta_{ml})      \dot{\Theta}_{ml} + L_{s}\sin(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} \\
  \dot{X}_{br} &= L_{t}\sin(\Theta_{bl})  \dot{\Theta}_{bl} + L_{s}\sin(\Theta_{ml})      \dot{\Theta}_{ml} + L_{s}\sin(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} + L_{t}\sin(\Theta_{br}-\pi)  \dot{\Theta}_{br}
\end{align}

@@

\section{Brownian Equations}
This section shows the velocity definitions using the Brownian dynamics equation. \\
\begin{align}  
  \dot{X}_{bl} &= 0 \\
  \dot{X}_{ml} &= \frac{1}{\gamma} \Big(F_{xml} + \mn \lambda_{ls}(X_{ml} - X_{bl}) + \lambda_{lt}(X_{t } - X_{ml}) \Big) + R_{xml} \\
  \dot{X}_{t } &= \frac{1}{\gamma} \Big(F_{xt } + \mn \lambda_{lt}(X_{t } - X_{ml}) + \lambda_{rt}(X_{mr} - X_{t }) \Big) + R_{xt } \\
  \dot{X}_{mr} &= \frac{1}{\gamma} \Big(F_{xmr} + \mn \lambda_{rt}(X_{mr} - X_{t }) + \lambda_{rs}(X_{br} - X_{mr}) \Big) + R_{xmr} \\
  \dot{X}_{br} &= \frac{1}{\gamma} \Big(F_{xbr} + \mn \lambda_{rs}(X_{br} - X_{mr})                                 \Big) + R_{xbr}
\end{align}

@@

\section{Expanded Brownian Equations}

\begin{align}
  &L_{t}\sin(\Theta_{bl})  \dot{\Theta}_{bl} = \frac{1}{\gamma}F_{xml} + \mn\frac{1}{\gamma}\lambda_{ls}(X_{ml} - X_{bl}) + \frac{1}{\gamma}\lambda_{lt}(X_{t } - X_{ml}) + R_{xml} \\
  &L_{t}\sin(\Theta_{bl})  \dot{\Theta}_{bl} + L_{s}\sin(\Theta_{ml})      \dot{\Theta}_{ml} = \frac{1}{\gamma}F_{xt } + \mn\frac{1}{\gamma}\lambda_{lt}(X_{t } - X_{ml}) + \frac{1}{\gamma}\lambda_{rt}(X_{mr} - X_{t }) + R_{xt } \\
  &L_{t}\sin(\Theta_{bl})  \dot{\Theta}_{bl} + L_{s}\sin(\Theta_{ml})      \dot{\Theta}_{ml} + L_{s}\sin(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} = \frac{1}{\gamma}F_{xmr} + \mn\frac{1}{\gamma}\lambda_{rt}(X_{mr} - X_{t }) + \frac{1}{\gamma}\lambda_{rs}(X_{br} - X_{mr}) + R_{xmr} \\
  &L_{t}\sin(\Theta_{bl})  \dot{\Theta}_{bl} + L_{s}\sin(\Theta_{ml})      \dot{\Theta}_{ml} + L_{s}\sin(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} + L_{t}\sin(\Theta_{br}-\pi)  \dot{\Theta}_{br} = \frac{1}{\gamma}F_{xbr} + \mn\frac{1}{\gamma}\lambda_{rs}(X_{br} - X_{mr}) + R_{xbr}
\end{align}

\begin{align}
  &\mn L_{t}\cos(\Theta_{bl})  \dot{\Theta}_{bl} = \frac{1}{\gamma}F_{yml} + \mn \frac{1}{\gamma}\lambda_{ls}(Y_{ml} - Y_{bl}) + \frac{1}{\gamma}\lambda_{lt}(Y_{t } - Y_{ml}) + R_{yml} \\
  &\mn L_{t}\cos(\Theta_{bl})  \dot{\Theta}_{bl} + \mn L_{s}\cos(\Theta_{ml})  \dot{\Theta}_{ml}  = \frac{1}{\gamma}F_{yt } + \mn \frac{1}{\gamma}\lambda_{lt}(Y_{t } - Y_{ml}) + \frac{1}{\gamma}\lambda_{rt}(Y_{mr} - Y_{t }) + R_{yt } \\
  &\mn L_{t}\cos(\Theta_{bl})  \dot{\Theta}_{bl} + \mn L_{s}\cos(\Theta_{ml})  \dot{\Theta}_{ml} + \mn L_{s}\cos(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} = \frac{1}{\gamma}F_{ymr} + \mn \frac{1}{\gamma}\lambda_{rt}(Y_{mr} - Y_{t }) + \frac{1}{\gamma}\lambda_{rs}(Y_{br} - Y_{mr}) + R_{ymr} \\
  &\mn L_{t}\cos(\Theta_{bl})  \dot{\Theta}_{bl} + \mn L_{s}\cos(\Theta_{ml})  \dot{\Theta}_{ml} + \mn L_{s}\cos(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} + \mn L_{t}\cos(\Theta_{br}-\pi)  \dot{\Theta}_{br} = \frac{1}{\gamma}F_{ybr} + \mn \frac{1}{\gamma}\lambda_{rs}(Y_{br} - Y_{mr}) + R_{ybr}
\end{align}

\section{System after Subtracting out Angular Velocity Terms}
This is the system after subtracting equations from each other to eliminate some angular velocity terms.\\

\begin{align}
  L_{t}\sin(\Theta_{bl})      \dot{\Theta}_{bl} &= \frac{1}{\gamma}F_{xml} - \frac{1}{\gamma}\lambda_{ls}(X_{ml} - X_{bl}) + \frac{1}{\gamma}\lambda_{lt}(X_{t } - X_{ml}) + R_{xml} \\
  L_{s}\sin(\Theta_{ml})      \dot{\Theta}_{ml} &= \frac{1}{\gamma}F_{xt } - \frac{2}{\gamma}\lambda_{lt}(X_{t } - X_{ml}) + \frac{1}{\gamma}\lambda_{rt}(X_{mr} - X_{t }) + R_{xt } - \frac{1}{\gamma}F_{xml} - \mn\frac{1}{\gamma}\lambda_{ls}(X_{ml} - X_{bl}) - R_{xml} \\
  L_{s}\sin(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} &= \frac{1}{\gamma}F_{xmr} - \frac{2}{\gamma}\lambda_{rt}(X_{mr} - X_{t }) + \frac{1}{\gamma}\lambda_{rs}(X_{br} - X_{mr}) + R_{xmr} - \frac{1}{\gamma}F_{xt } - \mn\frac{1}{\gamma}\lambda_{lt}(X_{t } - X_{ml}) - R_{xt } \\
  L_{t}\sin(\Theta_{br}-\pi)  \dot{\Theta}_{br} &= \frac{1}{\gamma}F_{xbr} - \frac{2}{\gamma}\lambda_{rs}(X_{br} - X_{mr}) + R_{xbr} - \frac{1}{\gamma}F_{xmr} - \mn\frac{1}{\gamma}\lambda_{rt}(X_{mr} - X_{t }) - R_{xmr} 
\end{align}

\begin{align}
  \mn L_{t}\cos(\Theta_{bl})      \dot{\Theta}_{bl} &= \frac{1}{\gamma}F_{yml} - \frac{1}{\gamma}\lambda_{ls}(Y_{ml} - Y_{bl}) + \frac{1}{\gamma}\lambda_{lt}(Y_{t } - Y_{ml}) + R_{yml} \\
  \mn L_{s}\cos(\Theta_{ml})      \dot{\Theta}_{ml} &= \frac{1}{\gamma}F_{yt } - \frac{2}{\gamma}\lambda_{lt}(Y_{t } - Y_{ml}) + \frac{1}{\gamma}\lambda_{rt}(Y_{mr} - Y_{t }) + R_{yt } - \frac{1}{\gamma}F_{yml} - \mn \frac{1}{\gamma}\lambda_{ls}(Y_{ml} - Y_{bl}) - R_{yml}\\
  \mn L_{s}\cos(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} &= \frac{1}{\gamma}F_{ymr} - \frac{2}{\gamma}\lambda_{rt}(Y_{mr} - Y_{t }) + \frac{1}{\gamma}\lambda_{rs}(Y_{br} - Y_{mr}) + R_{ymr} - \frac{1}{\gamma}F_{yt } - \mn \frac{1}{\gamma}\lambda_{lt}(Y_{t } - Y_{ml}) - R_{yt } \\
  \mn L_{t}\cos(\Theta_{br}-\pi)  \dot{\Theta}_{br} &= \frac{1}{\gamma}F_{ybr} - \frac{2}{\gamma}\lambda_{rs}(Y_{br} - Y_{mr}) + R_{ybr} - \frac{1}{\gamma}F_{ymr} - \mn \frac{1}{\gamma}\lambda_{rt}(Y_{mr} - Y_{t }) - R_{ymr} 
\end{align}

\section{System of Equations}
This section creates a system of equations by equating the Cartesian and Brownian velocity definitions from above. \\

@@

\section{System after Addition}
By adding coordinates for br to mr, mr to t, and t to ml, we simplify one side of our equations. \\

@@

\section{Solution for $\dot{\Theta}_{br}$}
The following sections come up with solutions for $\dot{\Theta}_{br}$, $\dot{\Theta}_{mr}$, $\dot{\Theta}_{ml}$ and $\dot{\Theta}_{bl}$ using the equations we found in the previous section. \\

@@

\begin{multline}
\dot{\Theta}_{bl} =
\frac{1}{L_t}\cos(\Theta_{bl})\Big(\dot{Y}_{bl} + \dot{Y}_{t } + \dot{Y}_{mr} + \dot{Y}_{br}
- \frac{1}{\gamma}F_{yml} - \frac{1}{\gamma}F_{yt } - \frac{1}{\gamma}F_{ymr} - \frac{1}{\gamma}F_{ybr} - R_{yml} - R_{yt} - R_{ymr} - R_{ybr} \Big)\\
- \frac{1}{L_t}\sin(\Theta_{bl})\Big(\dot{X}_{bl} + \dot{X}_{t } + \dot{X}_{mr} + \dot{X}_{br}
 - \frac{1}{\gamma}F_{xml} - \frac{1}{\gamma}F_{xt } - \frac{1}{\gamma}F_{xmr} - \frac{1}{\gamma}F_{xbr} - R_{xml} - R_{xt } - R_{xmr} - R_{xbr} \Big)
\end{multline}
